Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-28 paper.tex
aa summary

    \section{Automatic Analysis}
        \subsection{Summary}
        Automatic analysis (aa) is another Matlab-based modular workflow engine,
having started of as a pipelining system for SPM. User may define their pipeline
through a Matlab user script and specify the tasks in addition to their input
and output types through an XML module interface. Modules used in pipelines must
be integrated into aa which can be easily accomplished through XML interfaces. It is also possible to easily
parallelize the code in qsub, if required. 
        \subsection{Pipeline description}
        aa pipelines have two main components: 1) the Matlab user script and 2)
the XML tasklist. The user script is a script that defines which data will be
processed, any necessary parameter, and how it will be processed. aa provides an example user script,
which can be modified to meet user's needs. The entire pipeline in aa is defined
in a single structure, known as aap, which makes the task of record-keeping
simple.

@@

        In order to ensure that the correct output data is being operated on,
each task is provided with its own unique folder. The aa engine will ensure that
the necessary input data is located in the folder before task execution and also
acquiring the outputs after task completion.

        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Dipy}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Make}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Pydiper}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

>>>>

    \section{Automatic Analysis}
        \subsection{Summary}
        Automatic analysis (aa) is another Matlab-based modular workflow engine,
having started of as a workflow engine for SPM. User may define their pipeline
through a Matlab user script and specify the tasks in addition to their input
and output types through an XML module interface. Modules used in pipelines must
be integrated into aa which can be easily accomplished through XML interfaces.
aa workflows can be executed locally, or in parallel through qsub or condor.

        \subsection{Pipeline description}
        aa pipelines have two main components: 1) the Matlab user script and 2)
the XML tasklist. The user script is a script that defines which data will be
processed, any necessary parameter, and how it will be processed. aa provides an example user script,
which can be modified to meet user's needs. The entire pipeline in aa is defined
in a single structure, known as aap, which makes the task of record-keeping
simple.

@@

        In order to ensure that the correct output data is being operated on,
each task is provided with its own unique folder. The aa engine will transmit
the necessary input data to the folder before task execution and also
acquiring the outputs after task completion. Output folders are numbered such
that if a given module is invoked multiple times, each of those folders are
assigned an incremental ordering corresponding to the order in which they have been
executed \note{sentence might not make sense}. Should all data be required for
each task in the tasklist, all the data will be copied to each task folder.

    Similarly to a pipeline, each module is comprised of an XML interface and a
Matlab source file. A module's XML file consist of specifications on required input
and output modalities, as well as the desired domain. One of the most important
properties include the domain at which the module operates. While there exist mainy domains for
modules and new ones can easily be created and integrated by the user, the most
prominently used ones include: "study", "subject", "session". As their name suggests, a
module with the domain "study" will only be executed once for each time it
appears in the tasklist, whereas "subject" executes the module for each subject
within the task and "session" executes once for each session within a subject.

    In addition to module domains, another important module property is the
input and output data stream types. Data stream types denote what input and
output data type each module produces. Commonly used data stream
types include "epi", "structural" and "dicom\_header".

    Optional fields specified in a module include qsub, for estimates of
requirements for parallel processing,
and \textit{performanceoutput}, for garbage collection.

   Analysis parameters can easily be configured in aa. Any variable defined by
the \textit{aaprecipe} command may be modified. Parameters can also be defined
for an instance of a module within the XML tasklist. Alternatively, it is also
possible to create an XML file that inherits parameters from another XML file
and overrides some or all of the parameters.

   To set defaults and site-specific configurations, it is possible to either
create a local config file or by creating another parameter default file which
inherits the original one.

    aa also supports the creation of branched tasklist. This allows a section of
the pipeline steps to undergo different tasks or the same tasks in a different
order in one pipeline rather than having to create separate pipelines.

        \subsection{Pipeline execution}
        Once the definition of the user-script, XML tasklist and modules is
complete, the pipeline is ready for execution. Dependencies in aa are
established based on input and output data stream types. The aa engine attempts
to match the last task executed with a corresponding data stream type to the
current type. It is, however, possible to specify which module provides the
input to the current module by using fully qualified stream references.

        During execution, a map of all the modules that need to be executed and
their respective dependencies is generated. Modules that have completed contain
a flag file indicating their completion within their instance's root directory. Such
modules will not be re-executed by the engine.
Additionally, if it is required that a previous module is re-executed, the done flag is
removed from all dependent modules.

        Should part of the processing be performed on a different server it is
possible to connect the pipelines together through an analysis script. The aa engine will be reponsible for
matching the data streams between the servers in order to avoid the copying of
data and modules.

        \subsection{Debugging and provenance}
        In order to retrace the steps of previous executions, aa keeps a
detailed record of the events that occurred. These detailes are stored in a
Matlab object \note{similarly to PSOM}, which permits reexcution of a previous
run or extraction of specific parameter values.

        Additionally, to verify the correctness of the results produced, aa
implements tools for quality control and comes with a dedicated module for
low-level quality control.

    \section{Make}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Pydiper}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}
